\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-24 doc/incertae_sedis.tex
Update.

\newcommand{\bdrcomment}[1]{{\color{blue} #1}\xspace}

@@

>>>>

\newcommand{\bdrcomment}[1]{{\color{cyan} #1}\xspace}

@@

\subsection{Placement causes broken taxa}
\bdrcomment{I duplicated section \ref{conflict} to here, since we might want
  to discuss Figure \ref{fig:Handling-incertae-sedis} in the intro to answer
  why anybody would care.  Or not.  But note that the section on the ``naive approach''
  asks basically this question.}

Synthesis with \emph{incertae sedis} taxa has the potential to resolve
uncertain taxon placements using information from phylogenies.
Since
phylogenies are ranked higher than taxonomy, they may place members of
incertae sedis clades as they wish even when we do not take into
account the semantics of incertae sedis taxa.
However, without the
incertae sedis semantics described above, placing a taxon $A$ within a
taxon $B$ results in conflict with taxon $B$ in the taxonomy.
This has
three main effects: \begin{enumerate}
    \item The edge leading to clade $B$ is lost.
    \item Any taxonomy-only children of $B$ are placed at the
        MRCA of the phylogenetically informed taxa, instead of at node $B$.
    \item The name for taxon $B$ is lost.
    \item We do not record $A$ as being placed within $B$.
\end{enumerate} In order to avoid a situation
where input phylogenies conflict with a large number of taxa when
\emph{incertae sedis} taxa are placed within them, we have previously
filtered \emph{incertae sedis} taxa from the taxonomy when
constructing all prior synthesis trees.
